---
title: Information-based policy tools facilitate California farmers’ learning about
  nitrogen management
header-includes: \usepackage{graphicx} \usepackage{float}
output:
  word_document: default
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = "~/Box/irrigated_lands/")
library(ltm)
library(psych)
library(nnet)
library(dplyr)
library(tidyr)
library(VGAM)
library(reshape2)
library(stargazer)
library(lmtest)
library(pROC)
library(ggplot2)
library(jtools)
library(emmeans)
library(pscl)
library(vcd)
library(tinytex)
library(float)
library(extrafont)
library(cowplot)
```

```{r data, include = F, results = F}
components.df <- read.csv("cleaned_8.16.20_v4.csv")
model.df <- read.csv("modeldf_8.16.20_v4.csv") %>% select(-consulting2, -sequence3_lax_NMP, -sequence3_lax_FEP)
components.df$sequence3_strict_NMP <- factor(components.df$sequence3_strict_NMP, c('None', 'Conceptual', 'Applied'))
components.df$sequence3_strict_FEP <- factor(components.df$sequence3_strict_FEP, c('None', 'Conceptual', 'Applied'))
model.df$sequence3_strict_NMP <- factor(model.df$sequence3_strict_NMP, c('None', 'Conceptual', 'Applied'))
model.df$sequence3_strict_FEP <- factor(model.df$sequence3_strict_FEP, c('None', 'Conceptual', 'Applied'))
```

```{r summary, include = F, results = F}
summary(model.df)
summary(exp(model.df$LogTotalFarm_acres))
```

```{r descriptives contd with proptables, include = F, results = F}
prop.table(table(components.df$Q21_Analyze_A))
prop.table(table(components.df$Q21_Analyze_B))
prop.table(table(components.df$Q21_Identify_A))
prop.table(table(components.df$Q21_Identify_B))
prop.table(table(components.df$Q21_Improve_A))
prop.table(table(components.df$Q21_Improve_B))
prop.table(table(components.df$Q21_Changed_A))
prop.table(table(components.df$Q21_Changed_B))
```

\begin{table}[!h]
\centering
\begin{tabular}{lcccc}
\multicolumn{5}{l}{Table 1a. Independent variable summary statistics}                                                                                      \\ \hline
                                       & Mean                   & Median               & Min                  & Max                  \\ \cline{2-5}
*Farm and farmer resources*            &                        &                      &                      &                      \\
Farm Size (acres)                      & 355                    & 52                   & 1                    & 11,969               \\
Income                                 & \$100-200K             & \$100-200K           & < \$50K              & > \$1M                \\
Education                              & Associate degree     & Associate degree   & Primary school    & Graduate degree   \\
*Awareness, attitudes, and perceptions*&                        &                      &                      &                      \\
Aware of ag. impact                    & 3.47                   & 3.33                 & 1                    & 5                    \\
Stewardship attitudes                  & 3.86                   & 4                    & 1                    & 5                    \\
Farm-as-business attitudes             & 4.2                    & 4.4                  & 1                    & 5                    \\
Coalition perception                   & 3.48                   & 3.43                 & 1                    & 5                    \\
*Informational support*                &                        &                      &                      &                      \\
Information source count               & 3.38                   & 3                    & 0                    & 15                   \\
Attends self-certification course      & 0.57                   & 1                    & 0                    & 1                    \\
                                       & \multicolumn{1}{l}{}   & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ 
\multicolumn{5}{l}{Table 1b. Learning statements: proportions of respondents in each category. The NMP/FEP...}                                                 \\ 
\hline
\multicolumn{2}{l}{}                                                                  & No                   & Sometimes            & Yes                  \\ \cline{3-5} 
\multicolumn{2}{l}{Helps me analyze connections between N use and water movement}     & 0.36/0.40            & 0.32/0.32            & 0.32/0.28            \\
\multicolumn{2}{l}{Helps me identify areas in my operations for increased efficiency} & 0.36/0.40            & 0.34/0.32            & 0.30/0.28            \\
\multicolumn{2}{l}{Helps me improve my N management}                                  & 0.31/0.38            & 0.34/0.33            & 0.35/0.29            \\
\multicolumn{2}{l}{Has made me change my farm management significantly}               & 0.64/0.63            & 0.26/0.27            & 0.10/0.10            \\
                                                 & \multicolumn{1}{l}{}               & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ 
\multicolumn{5}{l}{Table 1c. Learning stages: proportions of respondents in each category for NMP/FEP}                                                \\
\hline

                                                 & \multicolumn{1}{l}{}               & None                 & Conceptual           & Applied              \\ \cline{3-5} 
\multicolumn{2}{l}{Learning stage}                                                    & 0.29/0.35            & 0.37/0.30            & 0.34/0.35           
\end{tabular}
\end{table}
\pagebreak 

## In Markdown

| Table 1a. Independent variable summary statistics                                          |                  |                  |                |                 |
|--------------------------------------------------------------------------------------------|:----------------:|:----------------:|:--------------:|:---------------:|
|                                                                                            |       Mean       |      Median      |       Min      |       Max       |
| *Farm and farmer resources*                                                                |                  |                  |                |                 |
| Farm Size (acres)                                                                          |        355       |        52        |        1       |      11,969     |
| Income                                                                                     |    \$100-200K    |    \$100-200K    |     < \$50K    |      > \$1M     |
| Education                                                                                  | Associate degree | Associate degree | Primary school | Graduate degree |
| *Awareness, attitudes, and perceptions*                                                    |                  |                  |                |                 |
| Aware of ag. impact                                                                        |       3.47       |       3.33       |        1       |        5        |
| Stewardship attitudes                                                                      |       3.86       |         4        |        1       |        5        |
| Farm-as-business attitudes                                                                 |        4.2       |        4.4       |        1       |        5        |
| Coalition perception                                                                       |       3.48       |       3.43       |        1       |        5        |
| *Informational support*                                                                    |                  |                  |                |                 |
| Information source count                                                                   |       3.38       |         3        |        0       |        15       |
| Attends self-certification course                                                          |       0.57       |         1        |        0       |        1        |
|                                                                                            |                  |                  |                |                 |
| Table 1b. Learning statements: proportions of respondents in each category. The NMP/FEP... |                  |                  |                |                 |
|                                                                                            |                  |        No        |    Sometimes   |       Yes       |
| Helps me analyze connections between N use and water movement                              |                  |     0.36/0.40    |    0.32/0.32   |    0.32/0.28    |
| Helps me identify areas in my operations for increased efficiency                          |                  |     0.36/0.40    |    0.34/0.32   |    0.30/0.28    |
| Helps me improve my N management                                                           |                  |     0.31/0.38    |    0.34/0.33   |    0.35/0.29    |
| Has made me change my farm management significantly                                        |                  |     0.64/0.63    |    0.26/0.27   |    0.10/0.10    |
|                                                                                            |                  |                  |                |                 |
| Table 1c. Learning stages: proportions of respondents in each category for NMP/FEP         |                  |                  |                |                 |
|                                                                                            |                  |       None       |   Conceptual   |     Applied     |
| Learning stage                                                                             |                  |     0.29/0.35    |    0.37/0.30   |    0.34/0.35    |


```{r learning stages plots, include = F, results = F}

#NMP
dfplan <- components.df %>%
  pivot_longer(
    cols = NMP_improve:NMP_changed,
    names_to = "plan_sentiment",
    values_to = "plan_score",
    values_drop_na = TRUE)

levels(dfplan$sequence3_strict_NMP) <- c('No\nlearning', 'Conceptual\nlearning', 'Applied\nlearning')

dfplan <- dfplan %>% 
  dplyr::select(plan_sentiment, plan_score, sequence3_strict_NMP)

dfplan$plan_sentiment_recode <-
  recode_factor(dfplan$plan_sentiment,
                "NMP_analyze"="Analyze", "NMP_identify"="Identify",
                 "NMP_improve"="Improve", "NMP_changed"="Change")

dfplan <- na.omit(dfplan)

p1 <- dfplan %>% 
  ggplot(aes(x = plan_sentiment_recode, fill = plan_score)) +
  geom_bar(stat="count") + facet_wrap(~ sequence3_strict_NMP) +
  scale_fill_manual(values=c("#D9D9D9", "#969696", "#525252")) + 
  labs(x = "Learning statements", y = "Number of farmers", 
       fill = "", title = "Nitrogen Management Plan") + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        axis.text = element_text(size = 10),
        plot.title = element_text(hjust = .5, vjust = 0, size = 10), 
        strip.background  = element_blank(), 
        legend.text = element_text(size = 10), 
        axis.text.x=element_text(angle = -45, hjust = 0)) +
   theme(legend.position = "none") +
  ylim(c(0,300)) 

# FEP
dfplan <- components.df %>%
  pivot_longer(
    cols = FEP_improve:FEP_changed,
    names_to = "plan_sentiment",
    values_to = "plan_score",
    values_drop_na = TRUE)

levels(dfplan$sequence3_strict_FEP) <- c('No\nlearning', 'Conceptual\nlearning', 'Applied\nlearning')

dfplan <- dfplan %>% 
  dplyr::select(plan_sentiment, plan_score, sequence3_strict_FEP)

dfplan$plan_sentiment_recode <- 
  recode_factor(dfplan$plan_sentiment, 
                "FEP_analyze"="Analyze", "FEP_identify"="Identify",
                "FEP_improve"="Improve", "FEP_changed"="Change")

dfplan <- na.omit(dfplan)

p2 <- dfplan %>% 
  mutate(plan_score = case_when(
    plan_score == "no" ~ "No",
    plan_score == "somewhat" ~ "Somewhat",
    plan_score == "yes" ~ "Yes"
  )) %>% 
  ggplot(aes(x = plan_sentiment_recode, fill = plan_score)) +
  geom_bar(stat="count") + facet_wrap(~ sequence3_strict_FEP) +  
  scale_fill_manual(values=c("#D9D9D9", "#969696", "#525252")) + 
  labs(x = "Learning statements", y = "Number of farmers", 
       fill = "Learning statement\nresponse", title = "Farm Evaluation Plan") + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        axis.text = element_text(size = 10),
        plot.title = element_text(hjust = .5, vjust = 0, size = 10), 
        strip.background  = element_blank(), 
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10),  
        axis.text.x=element_text(angle = -45, hjust = 0)) +
  ylim(c(0,300)) 
```

```{r learning stages grid arrange, results = "asis", echo = FALSE, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 3, fig.align="center"}
ggdraw() + draw_plot(p1, x = 0, y = 0, width = .4425, height = 1) +
           draw_plot(p2, x=.4425, y=0, width=0.5575, height = 1)
```

```{r full df models strict NMP, include = F, results = F}
strict.NMP <- model.df %>% 
  dplyr::select(-sequence3_strict_FEP)

modeldf.naomit = na.omit(strict.NMP)

NMP.model <- vglm(ordered(modeldf.naomit$sequence3_strict_NMP) ~ 
                    LogTotalFarm_acres + income + Education2 + 
                    blame_ag + priority_econ + priority_conservation + 
                    Info_count_15 + Q17_SelfCert_A + wqcperc_avg, 
                  data = modeldf.naomit, family=cratio(parallel = T))

# Parallel = F, Testing proportional odds assumption

NMP.model.np <- vglm(ordered(modeldf.naomit$sequence3_strict_NMP) ~  
                       LogTotalFarm_acres + income + Education2 +  
                       blame_ag + priority_econ + priority_conservation + 
                       Info_count_15 + Q17_SelfCert_A + wqcperc_avg, 
                     data = modeldf.naomit, family=cratio(parallel = F))

# Test prop odds
tran.LR <- deviance(NMP.model) - deviance(NMP.model.np)
degf <- NMP.model@df.residual - NMP.model.np@df.residual
p.value <- 1 - pchisq(q= tran.LR , df = degf); p.value
```

```{r full df models strict FEP, include = F, results = F}
strict.FEP <- model.df %>% 
  dplyr::select(-sequence3_strict_NMP)

modeldf.naomit <- na.omit(strict.FEP)

FEP.model <- vglm(ordered(modeldf.naomit$sequence3_strict_FEP) ~  
                   LogTotalFarm_acres + income + Education2 +  
                   blame_ag + priority_econ + priority_conservation + 
                   Info_count_15 + Q17_SelfCert_A + wqcperc_avg, 
                 data = modeldf.naomit, family=cratio(parallel = T))

FEP.model.np <- vglm(ordered(modeldf.naomit$sequence3_strict_FEP) ~  
                       LogTotalFarm_acres + income + Education2 +  
                        blame_ag + priority_econ + priority_conservation + 
                        Info_count_15 + Q17_SelfCert_A + wqcperc_avg, 
                      data = modeldf.naomit, family=cratio(parallel = F))

tran.LR <- deviance(FEP.model) - deviance(FEP.model.np)
degf <- FEP.model@df.residual - FEP.model.np@df.residual
p.value <- 1 - pchisq(q= tran.LR , df = degf); p.value
```

```{r, include = F, results = F}
summary(NMP.model.np)
summary(FEP.model.np)
```

```{r coeff table strict non-prop to put into latex NMP and FEP, include = F}
s1 <- summary(NMP.model.np)
nmpodds <- data.frame(exp(s1@coef3))
nmpci <- data.frame(exp(confint(NMP.model.np)))
nmp <- cbind(nmpodds, nmpci) 
nmp <- nmp %>% dplyr::select(Estimate, X2.5.., X97.5..) %>% round(3)
nmp <- cbind(rownames(nmp), data.frame(nmp, row.names=NULL))
nmp <- nmp %>% rename("variable" = "rownames(nmp)", "LCI" = "X2.5..", "UCI" = "X97.5..")
nmp <- nmp %>% separate(variable, into = c("variable", "level"), sep = ":") %>%
  pivot_wider(names_from = level, values_from = c(Estimate, LCI, UCI)) %>%
  dplyr::select(variable, Estimate_1, LCI_1, UCI_1, Estimate_2, LCI_2, UCI_2)
nmp$CI1 <- paste(nmp$LCI_1,nmp$UCI_1, sep = ", ")
nmp$CI1 <- paste0("(", nmp$CI1, ")")
nmp$CI2 <- paste(nmp$LCI_2,nmp$UCI_2, sep = ", ")
nmp$CI2 <- paste0("(", nmp$CI2, ")")
nmp <- nmp %>% dplyr::select(variable, Estimate_1, CI1, Estimate_2, CI2)


s1 <- summary(FEP.model.np)
fepodds <- data.frame(exp(s1@coef3))
fepci <- data.frame(exp(confint(FEP.model.np)))
fep <- cbind(fepodds, fepci) 
fep <- fep %>% dplyr::select(Estimate, X2.5.., X97.5..) %>% round(3)
fep <- cbind(rownames(fep), data.frame(fep, row.names=NULL))
fep <- fep %>% rename("variable" = "rownames(fep)", "LCI" = "X2.5..", "UCI" = "X97.5..")
fep <- fep %>% separate(variable, into = c("variable", "level"), sep = ":") %>% pivot_wider(names_from = level, values_from = c(Estimate, LCI, UCI)) %>% dplyr::select(variable, Estimate_1, LCI_1, UCI_1, Estimate_2, LCI_2, UCI_2)
fep$CI1 <- paste(fep$LCI_1,fep$UCI_1, sep = ", ")
fep$CI1 <- paste0("(", fep$CI1, ")")
fep$CI2 <- paste(fep$LCI_2,fep$UCI_2, sep = ", ")
fep$CI2 <- paste0("(", fep$CI2, ")")
fep <- fep %>% dplyr::select(variable, Estimate_1, CI1, Estimate_2, CI2)

odds <- left_join(nmp, fep, by = "variable")
colnames(odds) <- c("Variable", "NMP Conceptual Est.", "NMP Conceptual CI", " NMP Applied Est.", "NMP Applied CI", "FEP Conceptual Est.", "FEP Conceptual CI", "FEP Applied Est.", "FEP Applied CI")
odds
```

\resizebox{\textwidth}{!}{
\begin{tabular}{lcccccccc}
\multicolumn{9}{l}{Table 2. Sequential logit exponentiated coefficients and confidence intervals for learning stages of NMP and FEP}                                                                                                                     \\ \hline
                      & \multicolumn{4}{c}{Nitrogen Management Plan (NMP)}                                                                            & \multicolumn{4}{c}{Farm Evaluation Plan (FEP)}                                                                       \\ \cline{2-9} 
                      & \multicolumn{2}{c}{Conceptual}                         & \multicolumn{2}{c}{Applied}                                    & \multicolumn{2}{c}{Conceptual}                        & \multicolumn{2}{c}{Applied}                            \\
                      & \multicolumn{1}{c}{Odds} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{Odds} & \multicolumn{1}{c|}{95\% CI}        & \multicolumn{1}{c}{Odds} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{Odds} & \multicolumn{1}{c}{95\% CI} \\ \cline{2-9} 
(Intercept)           & 0.005$^{***}$            & (0.001, 0.021)              & 0.473                    & \multicolumn{1}{l|}{(0.095, 2.371)} & 0.009$^{***}$            & (0.002, 0.039)              & 1.065                    & (0.173, 6.555)              \\
Farm size (log acres) & 0.952                    & (0.817, 1.11)               & 0.966                    & \multicolumn{1}{l|}{(0.837, 1.116)} & 0.985                    & (0.848, 1.144)              & 0.988                    & (0.84, 1.161)               \\
Income                & 0.882                    & (0.751, 1.035)              & 0.922                    & \multicolumn{1}{l|}{(0.795, 1.07)}  & 0.857$^{  .}$            & (0.733, 1.002)              & 0.975                    & (0.826, 1.151)              \\
Education             & 0.927                    & (0.81, 1.059)               & 0.854$^{*}$              & \multicolumn{1}{l|}{(0.749, 0.974)} & 0.899                    & (0.782, 1.032)              & 0.832$^{*}$              & (0.714, 0.968)              \\
Aware of ag. impact   & 1.51$^{***}$             & (1.225, 1.862)              & 1.347$^{**}$             & \multicolumn{1}{l|}{(1.102, 1.647)} & 1.491$^{***}$            & (1.207, 1.843)              & 1.377$^{**}$             & (1.093, 1.735)              \\
Stewardship attitude & 1.475$^{***}$            & (1.198, 1.817)              & 1.107                    & \multicolumn{1}{l|}{(0.874, 1.402)} & 1.43$^{**}$              & (1.155, 1.77)               & 1.052                    & (0.803, 1.378)              \\
Farm-as-business attitude  & 1.24                     & (0.951, 1.615)              & 0.722$^{*}$              & \multicolumn{1}{l|}{(0.538, 0.969)} & 1.198                    & (0.91, 1.579)               & 0.636$^{*}$              & (0.45, 0.899)               \\
Coalition perception  & 2.491$^{***}$            & (1.868, 3.322)              & 1.353$^{*}$              & \multicolumn{1}{l|}{(1.011, 1.81)}  & 2.205$^{***}$            & (1.659, 2.931)              & 1.245                    & (0.902, 1.72)                \\
Info. source count    & 1.075$^{  .}$            & (0.989, 1.168)              & 1.145$^{***}$            & \multicolumn{1}{l|}{(1.066, 1.23)}  & 1.085$^{*}$              & (1, 1.177)                  & 1.205$^{***}$            & (1.108, 1.312)              \\
Self-certification    & 1.788$^{**}$             & (1.192, 2.682)              & 1.207                    & \multicolumn{1}{l|}{(0.809, 1.802)} & 1.275                    & (0.849, 1.914)              & 1.154                    & (0.738, 1.804)   \\ \hline
\multicolumn{9}{l}{$^{*}$ p \textless 0.05,  $^{**}$ p \textless 0.01,  $^{***}$ p \textless 0.001}                                                                                    
\end{tabular}
}
\pagebreak 

## Markdown

| Table 2. Sequential logit exponentiated coefficients and confidence intervals for learning stages of NMP and FEP |
|------------------------------------------------------------------------------------------------------------------|:------------------------------:|:--------------:|:-------------:|:--------------:|:--------------------------:|:--------------:|:-------------:|:--------------:|
|                                                                                                                  | Nitrogen Management Plan (NMP) |                |               |                | Farm Evaluation Plan (FEP) |                |               |                |
|                                                                                                                  |           Conceptual           |                |    Applied    |                |         Conceptual         |                |    Applied    |                |
|                                                                                                                  |              Odds              |     95\% CI    |      Odds     |     95\% CI    |            Odds            |     95\% CI    |      Odds     |     95\% CI    |
| (Intercept)                                                                                                      |          0.005$^{***}$         | (0.001, 0.021) |     0.473     | (0.095, 2.371) |        0.009$^{***}$       | (0.002, 0.039) |     1.065     | (0.173, 6.555) |
| Farm size (log acres)                                                                                            |              0.952             |  (0.817, 1.11) |     0.966     | (0.837, 1.116) |            0.985           | (0.848, 1.144) |     0.988     |  (0.84, 1.161) |
| Income                                                                                                           |              0.882             | (0.751, 1.035) |     0.922     | (0.795, 1.07)  |        0.857$^{  .}$       | (0.733, 1.002) |     0.975     | (0.826, 1.151) |
| Education                                                                                                        |              0.927             |  (0.81, 1.059) |  0.854$^{*}$  | (0.749, 0.974) |            0.899           | (0.782, 1.032) |  0.832$^{*}$  | (0.714, 0.968) |
| Aware of ag. impact                                                                                              |          1.51$^{***}$          | (1.225, 1.862) |  1.347$^{**}$ | (1.102, 1.647) |        1.491$^{***}$       | (1.207, 1.843) |  1.377$^{**}$ | (1.093, 1.735) |
| Stewardship attitude                                                                                             |          1.475$^{***}$         | (1.198, 1.817) |     1.107     | (0.874, 1.402) |         1.43$^{**}$        |  (1.155, 1.77) |     1.052     | (0.803, 1.378) |
| Farm-as-business attitude                                                                                        |              1.24              | (0.951, 1.615) |  0.722$^{*}$  | (0.538, 0.969) |            1.198           |  (0.91, 1.579) |  0.636$^{*}$  |  (0.45, 0.899) |
| Coalition perception                                                                                             |          2.491$^{***}$         | (1.868, 3.322) |  1.353$^{*}$  | (1.011, 1.81)  |        2.205$^{***}$       | (1.659, 2.931) |     1.245     |  (0.902, 1.72) |
| Info. source count                                                                                               |          1.075$^{  .}$         | (0.989, 1.168) | 1.145$^{***}$ | (1.066, 1.23)  |         1.085$^{*}$        |   (1, 1.177)   | 1.205$^{***}$ | (1.108, 1.312) |
| Self-certification                                                                                               |          1.788$^{**}$          | (1.192, 2.682) |     1.207     | (0.809, 1.802) |            1.275           | (0.849, 1.914) |     1.154     | (0.738, 1.804) |
| $^{*}$ p < 0.05,  $^{**}$ p < 0.01,  $^{***}$ p < 0.001                                                          |                                |                |               |                |                            |                |               |                |

```{r NMP pp edu p1, include = FALSE}

modeldf.naomit <- na.omit(strict.NMP)

pp_df <- with(modeldf.naomit, 
              data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), 
                         income = median(income), 
                         Education2 = c(1:7), 
                         blame_ag = median(blame_ag), 
                         priority_econ = median(priority_econ, na.rm = T),
                         priority_conservation = median(priority_conservation),
                         Info_count_15 = median(Info_count_15, na.rm = T),
                         Q17_SelfCert_A = 1, 
                         wqcperc_avg = median(wqcperc_avg, na.rm = T)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(NMP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% 
  filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% 
  filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)


meltdf.clean$Level <- ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd <- position_dodge(.1)

p1 <- meltdf.clean %>% 
  ggplot(aes(x=Education2, y=Probability,
             ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + 
  facet_wrap(~Level) +
  labs(x = "Education level", y = "Predicted probabilities", 
       title = "Nitrogen Management Plan") + 
  scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(Education2, Conceptual, Applied) %>% 
  filter(Education2 == 4 | Education2 == 6)
pp_quartiles
```

```{r FEP pp edu p2, include = FALSE}

modeldf.naomit <- na.omit(strict.FEP)

pp_df <- with(modeldf.naomit, 
              data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), 
                         income = median(income), 
                         Education2 = c(1:7), 
                         blame_ag = median(blame_ag), 
                         priority_econ = median(priority_econ, na.rm = T),
                         priority_conservation = median(priority_conservation),
                         Info_count_15 = median(Info_count_15, na.rm = T),
                         Q17_SelfCert_A = 1, 
                         wqcperc_avg = median(wqcperc_avg, na.rm = T)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(FEP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% 
  filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% 
  filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)


meltdf.clean$Level <- ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd <- position_dodge(.1)

p2 <- meltdf.clean %>% 
  ggplot(aes(x=Education2, y=Probability, 
             ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + 
  facet_wrap(~Level) +
  labs(x = "Education level", y = "Predicted probabilities", 
       title = "Farm Evaluation Plan") + 
  scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(Education2, Conceptual, Applied) %>% 
  filter(Education2 == 4 | Education2 == 6)
pp_quartiles
```

```{r predicted probs 1, results = "asis", echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 2.5, fig.align="center"}
plot_grid(p1, p2, labels=c("a", "b"), ncol=2, nrow = 1, label_size = 10, label_fontfamily = "Times")
```

```{r NMP pp farm as business attitudes p2, include = FALSE}

modeldf.naomit <- na.omit(strict.NMP)

pp_df <- with(modeldf.naomit, 
              data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), 
                         income = median(income), 
                         Education2 = median(Education2), 
                         blame_ag = median(blame_ag), 
                         priority_econ = c(1:5), 
                         priority_conservation = median(priority_conservation),
                         Info_count_15 = median(Info_count_15, na.rm = T),
                         Q17_SelfCert_A = 1, 
                         wqcperc_avg = median(wqcperc_avg)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(NMP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% 
  filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% 
  filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)


meltdf.clean$Level <- ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd <- position_dodge(.1)

p2 <- meltdf.clean %>% 
  ggplot(aes(x=priority_econ, y=Probability, 
             ymin=LLvalue, ymax=ULvalue)) +
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + 
  facet_wrap(~Level) +
  labs(x = "Farm-as-business attitude", y = "Predicted probabilities", 
       title = "Nitrogen Management Plan") + 
  scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(priority_econ, Conceptual, Applied) %>% 
  filter(priority_econ == 4 | priority_econ == 5)

pp_quartiles
```

```{r NMP pp stewardship attitudes p3, include = FALSE}

modeldf.naomit <- na.omit(strict.NMP)

pp_df <- with(modeldf.naomit, 
              data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres),
                         income = median(income), 
                         Education2 = median(Education2), 
                         blame_ag = median(blame_ag), 
                         priority_econ = median(priority_econ),
                         priority_conservation = c(1:5), 
                         Info_count_15 = median(Info_count_15, na.rm = T),
                         Q17_SelfCert_A = 1, 
                         wqcperc_avg = median(wqcperc_avg)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(NMP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% 
  filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% 
  filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)


meltdf.clean$Level <- ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd = position_dodge(.1)

p3 <- meltdf.clean %>% 
  ggplot(aes(x=priority_conservation, y=Probability, 
             ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + 
  facet_wrap(~Level) +
  labs(x = "Stewardship attitude", y = "Predicted probabilities", 
       title = "Nitrogen Management Plan") + 
  scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(priority_conservation, Conceptual, Applied) %>% 
  filter(priority_conservation == 3 | priority_conservation == 5)

pp_quartiles
```

```{r NMP pp perc p4, include = FALSE}

modeldf.naomit <- na.omit(strict.NMP)

pp_df <- with(modeldf.naomit, 
              data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), 
                         income = median(income), 
                         Education2 = median(Education2), 
                         blame_ag = median(blame_ag), 
                         priority_econ = median(priority_econ, na.rm = T),
                         priority_conservation = median(priority_conservation),
                         Info_count_15 = median(Info_count_15, na.rm = T),
                         Q17_SelfCert_A = 1, 
                         wqcperc_avg = c(1:5)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(NMP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf = ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% 
  filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% 
  filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)

meltdf.clean$Level = ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd <- position_dodge(.1)

p4 <- meltdf.clean %>% 
  ggplot(aes(x=wqcperc_avg, y=Probability, 
             ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + 
  facet_wrap(~Level) +
  labs(x = "Coalition perception", y = "Predicted probabilities", 
       title = "Nitrogen Management Plan") + 
  scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(wqcperc_avg, Conceptual, Applied) %>% 
  filter(wqcperc_avg == 3 | wqcperc_avg == 4)

pp_quartiles
```

```{r NMP pp Information p5, include = FALSE}

modeldf.naomit <- na.omit(strict.NMP)

pp_df <- with(modeldf.naomit, 
              data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), 
                         income = median(income), 
                         Education2 = median(Education2), 
                         blame_ag = median(blame_ag), 
                         priority_econ = median(priority_econ, na.rm = T),
                         priority_conservation = median(priority_conservation),
                         Info_count_15 = c(0:15), 
                         Q17_SelfCert_A = 1, 
                         wqcperc_avg = median(wqcperc_avg)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(NMP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% 
  filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% 
  filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)
meltdf.clean$Level = ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))

pd <- position_dodge(.1)
p5 <- meltdf.clean %>% 
  ggplot(aes(x=Info_count_15, y=Probability,
               ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + 
  facet_wrap(~Level) +
  labs(x = "Information sources", y = "Predicted probabilities", 
       title = "Nitrogen Management Plan") + 
  scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank()) 

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(Info_count_15, Conceptual, Applied) %>% 
  filter(Info_count_15 == 2 | Info_count_15 == 5)

pp_quartiles
```

```{r FEP pp farm as business attitudes p6, include = FALSE}

modeldf.naomit <- na.omit(strict.FEP)

pp_df <- with(modeldf.naomit, 
              data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), 
                         income = median(income), 
                         Education2 = median(Education2), 
                         blame_ag = median(blame_ag), 
                         priority_econ = c(1:5), 
                         priority_conservation = median(priority_conservation),
                         Info_count_15 = median(Info_count_15, na.rm = T),
                         Q17_SelfCert_A = 1, 
                         wqcperc_avg = median(wqcperc_avg)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(FEP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)


meltdf.clean$Level <- ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd <- position_dodge(.1)

p6 <- ggplot(meltdf.clean, aes(x=priority_econ, y=Probability, 
                               ymin=LLvalue, ymax=ULvalue)) +
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + facet_wrap(~Level) +
  labs(x = "Farm-as-business attitude", y = "Predicted probabilities", 
       title = "Farm Evaluation Plan") + scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(priority_econ, Conceptual, Applied) %>% 
  filter(priority_econ == 4 | priority_econ == 5)

pp_quartiles
```

```{r FEP pp stewardship attitudes p7, include = FALSE}

modeldf.naomit <- na.omit(strict.FEP)

pp_df <- with(modeldf.naomit, data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), income = median(income), Education2 = median(Education2), blame_ag = median(blame_ag), priority_econ = median(priority_econ), priority_conservation = c(1:5), Info_count_15 = median(Info_count_15, na.rm = T), consulting2 = 0, Q17_SelfCert_A = 1, wqcperc_avg = median(wqcperc_avg)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(FEP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)


meltdf.clean$Level <- ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd = position_dodge(.1)

p7 <- ggplot(meltdf.clean, aes(x=priority_conservation, 
                               y=Probability, ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + facet_wrap(~Level) +
  labs(x = "Stewardship attitude", y = "Predicted probabilities", 
       title = "Farm Evaluation Plan") + scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(priority_conservation, Conceptual, Applied) %>% 
  filter(priority_conservation == 3 | priority_conservation == 5)

pp_quartiles
```

```{r FEP pp perc p8, include = FALSE}

modeldf.naomit <- na.omit(strict.FEP)

pp_df <- with(modeldf.naomit, data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), income = median(income), Education2 = median(Education2), blame_ag = median(blame_ag), priority_econ = median(priority_econ, na.rm = T), priority_conservation = median(priority_conservation), Info_count_15 = median(Info_count_15, na.rm = T), consulting2 = 0, Q17_SelfCert_A = 1, wqcperc_avg = c(1:5)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(FEP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf = ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)

meltdf.clean$Level = ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))
pd <- position_dodge(.1)

p8 <- ggplot(meltdf.clean, aes(x=wqcperc_avg, y=Probability, 
                               ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + facet_wrap(~Level) +
  labs(x = "Coalition perception", y = "Predicted probabilities", 
       title = "Farm Evaluation Plan") + scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank())

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(wqcperc_avg, Conceptual, Applied) %>% 
  filter(wqcperc_avg == 3 | wqcperc_avg == 4)

pp_quartiles
```

```{r FEP pp Information p9, include = FALSE}

modeldf.naomit <- na.omit(strict.FEP)

pp_df <- with(modeldf.naomit, data.frame(LogTotalFarm_acres = median(LogTotalFarm_acres), income = median(income), Education2 = median(Education2), blame_ag = median(blame_ag), priority_econ = median(priority_econ, na.rm = T), priority_conservation = median(priority_conservation), Info_count_15 = c(0:15), consulting2 = 0, Q17_SelfCert_A = 1, wqcperc_avg = median(wqcperc_avg)))

# Using predict function to get predicted probabilities, with standard errors
pp_pred <- cbind(pp_df, predict(FEP.model.np, newdata = pp_df, type = "link", se=TRUE))

fit1 <- pp_pred$`fitted.values.logitlink(P[Y>1|Y>=1])`
fit2 <- pp_pred$`fitted.values.logitlink(P[Y>2|Y>=2])`
se.fit1 <- pp_pred$`se.fit.logitlink(P[Y>1|Y>=1])`
se.fit2 <- pp_pred$`se.fit.logitlink(P[Y>2|Y>=2])`

ppdf_predCIs <- within(pp_pred, {
  Conceptual <- plogis(fit1)
  LL1 <- plogis(fit1 - (1.96 * se.fit1))
  UL1 <- plogis(fit1 + (1.96 * se.fit1))
  Applied <- plogis(fit2)
  LL2 <- plogis(fit2 - (1.96 * se.fit2))
  UL2 <- plogis(fit2 + (1.96 * se.fit2))
})

meltdf <- ppdf_predCIs %>% 
  gather(key = "Level", value = "Probability", 
         Conceptual, Applied, -UL1, -LL1, -UL2, -LL2) %>% 
  gather(key = "ULCI", value = "ULvalue", 
         UL1, UL2, -Level, -Probability, -LL1, -LL2) %>% 
  gather(key = "LLCI", value = "LLvalue", 
         LL1, LL2, -Level, -Probability, -ULCI, -ULvalue) 

meltdf1 <- meltdf %>% filter(Level == "Conceptual" & ULCI == "UL1" & LLCI == "LL1")
meltdf2 <- meltdf %>% filter(Level == "Applied" & ULCI == "UL2" & LLCI == "LL2")
meltdf.clean = rbind(meltdf1, meltdf2)
meltdf.clean$Level = ordered(meltdf.clean$Level, levels=c("Conceptual","Applied"))

pd <- position_dodge(.1)
p9 <- ggplot(meltdf.clean, aes(x=Info_count_15, y=Probability, 
                               ymin=LLvalue, ymax=ULvalue)) + 
  geom_ribbon(alpha=0.2) +
  geom_line(size=0.2) + facet_wrap(~Level) +
  labs(x = "Information sources", y = "Predicted probabilities", 
       title = "Farm Evaluation Plan") + scale_fill_brewer() + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank()) 

pp_quartiles <- ppdf_predCIs %>% 
  dplyr::select(Info_count_15, Conceptual, Applied) %>% 
  filter(Info_count_15 == 2 | Info_count_15 == 5)

pp_quartiles
```

```{r predicted probs 2, results = "asis", echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 10, fig.align="center"}
#grid.arrange(p3, p9, p2, p8, p6, p12, p4, p10, ncol = 2,  top=textGrob("Figure 3. Predicted probabilities of sequential logit: Attitudinal and informational variables across learning stages",gp=gpar(fontsize=10,fontfamily="Times"), x = 0, hjust = 0))

plot_grid(p3, p7, p2, p6, p4, p8, labels=c("a", "b", "c", "d", "e", "f"), ncol=2, nrow = 4, label_size = 10, label_fontfamily = "Times")
```
\pagebreak 

```{r predicted probs 3, results = "asis", echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 2.5, fig.align="center"}
plot_grid(p5, p9, labels=c("a", "b"), ncol=2, nrow = 1, label_size = 10, label_fontfamily = "Times")
```

```{r post-hoc visualizing information sources as sums, include = FALSE}

info <- components.df %>% dplyr::select(Q11_b_0:Q11_p_0, sequence3_strict_NMP)

info2 <- info %>%
  pivot_longer(
    cols = info$Q11_b_0:Q11_p_0,
    names_to = "info_source",
    values_to = "info_use",
    values_drop_na = TRUE)

info2$info_source_recode <- recode_factor(info2$info_source, "Q11_b_0"="Family", "Q11_c_0"="Field crew", "Q11_d_0"="Other growers", "Q11_e_0"="Irr. Distrct", "Q11_f_0"="Coalition", "Q11_g_0"="PCA", "Q11_h_0"="CCA", "Q11_i_0"="Ag. Commissioner", "Q11_j_0"="County FB", "Q11_k_0"="RCD", "Q11_l_0"="UC Ext.", "Q11_m_0"="CA FB", "Q11_n_0"="CDFA FREP", "Q11_o_0"="Comm. org/Co-op", "Q11_p_0"="NRCS")

info2 <- na.omit(info2)

infocount_none <- info2 %>% 
  filter(sequence3_strict_NMP == "None") %>% 
  group_by(info_source_recode) %>% 
  count(info_use) %>% 
  filter(info_use == 1) %>% 
  mutate(seq = "None")
infocount_conc <- info2 %>% 
  filter(sequence3_strict_NMP == "Conceptual") %>% 
  group_by(info_source_recode) %>% 
  count(info_use) %>% 
  filter(info_use == 1) %>% 
  mutate(seq = "Conceptual")
infocount_app <- info2 %>% 
  filter(sequence3_strict_NMP == "Applied") %>% 
  group_by(info_source_recode) %>% 
  count(info_use) %>% 
  filter(info_use == 1) %>% 
  mutate(seq = "Applied")

infocount <- rbind(infocount_none, infocount_conc, infocount_app)

pcount <- ggplot(infocount, aes(x = reorder(info_source_recode, -n), y = n)) +
  geom_bar(aes(fill = seq),stat = "identity", position = "dodge") + 
  scale_fill_brewer() + 
  labs(x = "Information source", y = "Number of farmers", fill = "") + 
  theme_classic() + 
  theme(text= element_text(size=12, family="Times"), 
        plot.title = element_text(hjust = .5, vjust = 0, size = 12), 
        strip.background  = element_blank(), legend.text = element_text(size = 8), 
        axis.text.x=element_text(angle = -45, hjust = 0))

infoclean <- na.omit(info)
infoclean$group <- factor(infoclean$sequence3_strict_NMP)

# Family -- none
pairwise.wilcox.test(infoclean$Q11_b_0, infoclean$group, p.adjust.method = "BH")
# Field crew -- none
pairwise.wilcox.test(infoclean$Q11_c_0, infoclean$group, p.adjust.method = "BH")
# Other growers -- between none-applied
pairwise.wilcox.test(infoclean$Q11_d_0, infoclean$group, p.adjust.method = "BH")
# Irr. dist -- none-conceptual, none-applied
pairwise.wilcox.test(infoclean$Q11_e_0, infoclean$group, p.adjust.method = "BH")
# Coalition -- all of them*
coalition <- pairwise.wilcox.test(infoclean$Q11_f_0, infoclean$group, p.adjust.method = "BH")
# PCA -- none-conceptual, none-applied
pca <- pairwise.wilcox.test(infoclean$Q11_g_0, infoclean$group, p.adjust.method = "BH")
# CCA-- between none-applied, conceptual-applied*
cca <- pairwise.wilcox.test(infoclean$Q11_h_0, infoclean$group, p.adjust.method = "BH")
# Ag Comm-- between none-applied, conceptual=applied*
agcomm <- pairwise.wilcox.test(infoclean$Q11_i_0, infoclean$group, p.adjust.method = "BH")
# County FB-- none-applied, conceptual=applied*
countyfb <- pairwise.wilcox.test(infoclean$Q11_j_0, infoclean$group, p.adjust.method = "BH")
# RCD -- none
pairwise.wilcox.test(infoclean$Q11_k_0, infoclean$group, p.adjust.method = "BH")
# UC EXt-- all but only 0.07 for conc-applied
ext <- pairwise.wilcox.test(infoclean$Q11_l_0, infoclean$group, p.adjust.method = "BH")
# CA FB-- all*
cafb <- pairwise.wilcox.test(infoclean$Q11_m_0, infoclean$group, p.adjust.method = "BH")
# CDFA-- none-conceptual, none-applied
cdfa <- pairwise.wilcox.test(infoclean$Q11_n_0, infoclean$group, p.adjust.method = "BH")
# Co-op-- none
pairwise.wilcox.test(infoclean$Q11_o_0, infoclean$group, p.adjust.method = "BH")
# NRCS-- none-applied
pairwise.wilcox.test(infoclean$Q11_p_0, infoclean$group, p.adjust.method = "BH")

# so of interest is: Coalition, CCA, Ag Comm, County FB, CA FB

library(ggsignif)
# pvalue between conceptual and applied
cca$p.value[1,1]
coalition$p.value[1,1]
agcomm$p.value[1,1]
countyfb$p.value[1,1]
cafb$p.value[1,1]

# pvalue between none and conceptual -- only coalition and cafb overlap
coalition$p.value[2,2]
pca$p.value[2,2]
ext$p.value[2,2]
cafb$p.value[2,2]
cdfa$p.value[2,2]

# In order
pca$p.value[2,2]
cca$p.value[1,1]
coalition$p.value[1,1]
coalition$p.value[2,2]
ext$p.value[2,2]
agcomm$p.value[1,1]
cdfa$p.value[2,2]
countyfb$p.value[1,1]
cafb$p.value[1,1]
cafb$p.value[2,2]

```

```{r post-hoc visualizing information sources as proportions, include = FALSE}
info2$sequence3_strict_NMP <- factor(info2$sequence3_strict_NMP, levels = c("None", "Conceptual", "Applied"))

sum.df <- info2 %>% 
  group_by(info_source_recode, sequence3_strict_NMP) %>% 
  count(info_use) %>% filter(info_use == 1) %>% select(-info_use)

prop.df <- sum.df %>% 
  group_by(info_source_recode) %>% 
  mutate(total = sum(n)) %>% 
  ungroup() %>% mutate(proportion = n/total)

diff.df <- prop.df %>% 
  group_by(info_source_recode) %>% 
  select(-n) %>% 
  pivot_wider(names_from = sequence3_strict_NMP, values_from = proportion) %>% 
  mutate(Conceptual_diff = Conceptual - None, Applied_diff = Applied - Conceptual) %>% 
  select(-None, -Conceptual, -Applied) %>% 
  pivot_longer(-c(info_source_recode, total), names_to = "Step", values_to = "Difference")

diff.df$Step <- factor(diff.df$Step, levels = c("Conceptual_diff", "Applied_diff"))
levels(diff.df$Step) <- c("Conceptual", "Applied")

# Proportions plot
pp <- ggplot(prop.df, aes(x = reorder(info_source_recode, -total), y = proportion)) + geom_bar(aes(fill = sequence3_strict_NMP),stat = "identity", position = "dodge") + scale_fill_manual(values=c("#D9D9D9", "#969696", "#525252")) + labs(x = "Information source", y = "Proportion of farmers using info source", fill = "") + theme_classic() + theme(text= element_text(size=14, family="Times"), plot.title = element_text(hjust = .5, vjust = 0, size = 12), strip.background  = element_blank(), legend.text = element_text(size = 10),  axis.text.x=element_text(angle = -45, hjust = 0))

```

```{r the info plots, results = "asis", echo = FALSE, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 5, fig.align="center"}

p2 <- pp + geom_signif(position = "identity",
  annotation = formatC(c("\u2020\u2020", "**", "***", "\u2020\u2020\u2020", 
                         "\u2020\u2020", "**", "\u2020\u2020", "**", "*", "\u2020")),
                xmin=c(.70, 3.00, 4.00, 3.70, 4.70, 8.00, 11.70, 13.00, 14.00, 13.70), 
                xmax=c(1.00, 3.30, 4.30, 4.00, 5.00, 8.30, 12.00, 13.30, 14.30, 14.00),
                y_position=c(0.4, 0.42, 0.495, 0.395, 0.395, 0.54, 0.40, 0.54, 0.55, 0.355), 
  tip_length = 0.01, size = .1, textsize = 4, family = "Times")

p2
```

